Chemically Self-Consistant Modeling of the Globular Cluster NGC 2808 and its Effects on the Inferred Helium abundance of Multiple Stellar Populations.

### 2024-02-03 ApJ/fidanka.tex
Final copy edits of NGC 2808 paper before submission

\begin{figure*}
	\centering
	\includegraphics[width=0.9\textwidth]{src/figures/notebookFigures/DensityMapDemo.png}
	\caption{Density map demo showing density estimate over different parts of
	the evolutionary sequence. The left panel shows the density map over the
	entire evolutionary sequence, while the middle panel shows the density map
	over the main sequence and the right most panel shows the density map over
	the RGB. Figures in the top row are the raw CMD, while figures in the
	bottom row are colored by the density map.}
	\label{densityMapDemo}
\end{figure*}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.45\textwidth]{src/figures/notebookFigures/DensityBinsDemo.png}
	\caption{CMD where points are colored by density. Lines show the
	density-color profile in each magnitude bin. In this figure adaptive
	binning targeted 1000 stars per bin}
	\label{densityBinsDemo}
\end{figure}

@@

\begin{figure*}
	\centering
	\includegraphics[width=0.9\textwidth]{Notebooks/Figures/BGMMMixingBin.pdf}
	\caption{Example of BGMM fit to a magnitude bin. The grey line shows the
	underlying color-density profile, while the black dashed-line shows the
	joint distribution of each BGMM component. The solid black lines show the
	two selected components.}
	\label{fig:BGMMDist}
\end{figure*}

\fidanka's BGMM method first breaks down the verticalized CMD into magnitude
bins with uniform numbers of stars per bin (here we adopt 250). Any stars left
over are placed into the final bin. For each bin a BGMM model with a maximum of
5 populations is fit to the color density profile. The number of populations is
then inferred from the weighting parameter (the mixing probability) of each
population. If the weighting parameter of any $k^{th}$ components less than
{\color{blue}0.05}, then that component is considered to be spurious and
removed. Additionally, if the number of populations in the bin above and the
bin below are the same, then the number of populations in the current bin is
forced to be the same as the number of populations in the bin above. Finally,
the initial guess fiducial line is added back to the BGMM inferred line. Figure
\ref{fig:vertFit} shows the resulting fiducial line(s) in each magnitude bin
for both a verticalized CMD and a non verticalized CMD.

\begin{figure}
	\centering
	\includegraphics[width=0.45\textwidth]{Notebooks/Figures/vertFit.png}
	\caption{CMD where points are colored by density. Lines trace the infered 
	fiducial line(s) in each magnitude bin.}
	\label{fig:vertFit}
\end{figure}

This method of fiducial line extraction effectively discriminated between
multiple populations long the main sequence and RGB of a cluster, while
simultaneously allowing for the presence of a single population along the MSTO
and subgiant branch.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{src/figures/ExtractedIsoFit.pdf}
  \caption{Synthetic population generated by fidanka at 10000pc with E(B-V) = 0, and an age of 12 Gyr along with the best fitting isochrone. The best fit paremeters are derived to be $mu=15.13$, E(B-V)=0.001, and an age of 12.33 Gyr.}
  \label{fig:ValidationBestFit}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{src/figures/DistributionOfErrors.pdf}
  \caption{Percent Error distribution for each of the three deriver parameters. Note that these values will be sensitive to the magnitude uncertainties of the photometry. Here we made use of the ACS artificial star tests to estimate the uncertanties. {\color{blue}Note that currently this is built with 100 runs, these take a long time so currently re running with 1000 runs.}}
  \label{fig:validationDist}
\end{figure}

>>>>

\begin{figure*}
	\centering
	\includegraphics[width=0.9\textwidth]{src/DensityMapDemo.png}
	\caption{Density map demo showing density estimate over different parts of
	the evolutionary sequence. The left panel shows the density map over the
	entire evolutionary sequence, while the middle panel shows the density map
	over the main sequence and the right most panel shows the density map over
	the RGB. Figures in the top row are the raw CMD, while figures in the
	bottom row are colored by the density map.}
	\label{densityMapDemo}
\end{figure*}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.45\textwidth]{src/DensityBinsDemo.png}
	\caption{CMD where point brightness is determined by local density. Lines show the
	density-color profile in each magnitude bin. In this figure adaptive
	binning targeted 1000 stars per bin}
	\label{densityBinsDemo}
\end{figure}

@@

\begin{figure*}
	\centering
	\includegraphics[width=0.9\textwidth]{BGMMMixingBin.pdf}
	\caption{Example of BGMM fit to a magnitude bin. The grey line shows the
	underlying color-density profile, while the black dashed-line shows the
	joint distribution of each BGMM component. The solid black lines show the
	two selected components.}
	\label{fig:BGMMDist}
\end{figure*}

\fidanka's BGMM method first breaks down the verticalized CMD into magnitude
bins with uniform numbers of stars per bin (here we adopt 250). Any stars left
over are placed into the final bin. For each bin a BGMM model with a maximum of
5 populations is fit to the color density profile. The number of populations is
then inferred from the weighting parameter (the mixing probability) of each
population. If the weighting parameter of any $k^{th}$ components less than
{\color{blue}0.05}, then that component is considered to be spurious and
removed. Additionally, if the number of populations in the bin above and the
bin below are the same, then the number of populations in the current bin is
forced to be the same as the number of populations in the bin above. Finally,
the initial guess fiducial line is added back to the BGMM inferred line. Figure
\ref{fig:vertFit} shows the resulting fiducial line(s) in each magnitude bin
for both a verticalized CMD and a non verticalized CMD. In contrast to other
work in the literature where evidence for up to 5 distinct populations has been
found; we only find evidence for two stellar populations.

\begin{figure}
	\centering
	\includegraphics[width=0.45\textwidth]{vertFit.png}
  \caption{Verticalized CMD where point brightness is determined by density
  (top). CMD where point brightness is determined by density, calculated
  fiducial lines are shown (bottom). The data used is from the Hubble Space
  Telescope UV Legacy Survey of Galactic Globular Clusters.}
	\label{fig:vertFit}
\end{figure}

This method of fiducial line extraction effectively discriminated between
multiple populations along the main sequence and RGB of a cluster, while
simultaneously allowing for the presence of a single population along the MSTO
and subgiant branch.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{src/ExtractedIsoFit.pdf}
  \caption{Synthetic population generated by fidanka at 10000pc with E(B-V) =
  0, and an age of 12 Gyr along with the best fitting isochrone. The best fit
  paremeters are derived to be $mu=15.13$, E(B-V)=0.001, and an age of 12.33
  Gyr.}
  \label{fig:ValidationBestFit}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{src/DistributionOfErrors.pdf}
  \caption{Percent Error distribution for each of the three deriver parameters.
  Note that these values will be sensitive to the magnitude uncertainties of
  the photometry. Here we made use of the ACS artificial star tests to estimate
  the uncertanties.}
  \label{fig:validationDist}
\end{figure}

### 2024-02-03 ApJ/modeling.tex
Final copy edits of NGC 2808 paper before submission

\section{Stellar Models}\label{sec:modeling}
We use the Dartmouth Stellar Evolution Program \citep[DSEP, ][]{Dotter2008} to
generate stellar models. DSEP is a well-tested, one-dimensional stellar
evolution code which includes a mixing length model of convection,
gravitational settling, and diffusion. Using the solar composition presented in
\citep{Grevesse2007} (GAS07), MARCS model atmosphers, OPLIB high temperature
opacities, and AESOPUS 2.0 low temperautre opacities we find a solar calibrated
mixing length parameter, $\alpha_{MLT}$, of $\alpha_{MLT} = 1.901$.

We use DSEP to evolve stellar models ranging in mass from 0.3 to 2.0 solar
masses from the zero-age main sequence (ZAMS) to the tip of the red giant
branch. Below 0.7 $M_{\odot}$ we evolve a model every 0.03 $M_{\odot}$ and
above 0.7 $M_{\odot}$ we evolve a model every 0.5 $M_{\odot}$. Additionally, we
evolve models over a grid of mixing length parameters from $\alpha_{MLT} = 1.0$
to $\alpha_{MLT} = 2.0$ in steps of 0.1. In addition to the mixing length grid
the evolved grid of models also has dimensions population (A or E) (Table
\ref{tab:comp}) and helium abundance ($Y=0.24, 0.27, 0.3, 0.33, 0.36, 0.39$).
Each model is evolved in DSEP with typical numeric tolerences of one part in
{\color{red}WHAT}, and an average of {\color{red} WHAT} shells. Each model is
allowed a maximum time step of 50 Myr.

>>>>

\section{Stellar Models}\label{sec:modeling}
We use the Dartmouth Stellar Evolution Program \citep[DSEP, ][]{Dotter2008} to
generate stellar models. DSEP is a one-dimensional stellar
evolution code which includes a mixing length model of convection,
gravitational settling, and diffusion. Using the solar composition presented in
\citep{Grevesse2007} (GAS07), MARCS model atmosphers, OPLIB high temperature
opacities, and AESOPUS 2.0 low temperautre opacities we find a solar calibrated
mixing length parameter, $\alpha_{MLT}$, of $\alpha_{MLT} = 1.901$.

We use DSEP to evolve stellar models ranging in mass from 0.3 to 2.0 solar
masses from the fully convective pre-main sequence to the tip of the red giant
branch. Below 0.7 $M_{\odot}$ we evolve a model every 0.03 $M_{\odot}$ and
above 0.7 $M_{\odot}$ we evolve a model every 0.05 $M_{\odot}$. We evolve
models over a grid of mixing length parameters from $\alpha_{MLT} = 1.0$ to
$\alpha_{MLT} = 2.0$ in steps of 0.1. For each mixing length, a grid of models
and isochrones were calculated, with chemical compositions consistent with
Populations A and E (see Table \ref{tab:comp}) and a range of helium abundances
(Y=0.24, 0.27, 0.30, 0.33, 0.36, and 0.39). In total,144 sets of isochrones,
each with a unique composition and mixing length were calculated. Each model is
evolved in DSEP with typical numeric tolerences of one part in $10^{7}$. Each
model is allowed a maximum time step of 50 Myr.

### 2024-02-03 ArXiv/AtmopshericModels.tex
Final copy edits of NGC 2808 paper before submission

\subsection{Atmospheric Boundary Conditions}\label{sec:atm}
Certain assumptions, primarily that the radiation field is at equilibirum and radiative transport is diffusive \citep{Salaris2005}, made in stellar structure
codes, such as DSEP, are valid when the optical depth of a star is small.
However, in the atmospheres of stars, the number density of particles drops low
enough and the optical depth consequently becomes large enough that these
assumptions break down, and separate, more physically motivated, plasma modeling code is required.
Generally structure code will use tabulated atmospheric boundary conditions
generated by these specialized codes ATLAS9 \citep{Kurucz1993}, PHEONIX \citep{Husser2013}, MARCS \citep{Gustafsson2008}, and MPS-ATLAS \citep{Kostogryz2023}. Often, as the boundary conditions are both expensive to compute
and not the speciality of stellar structure researchers, the boundary
conditions are not updated as as light-element interior abundance varies.

One key element when chemically consistently modeling NGC 2808 modeling is the
incorporation of new atmospheric models with the same elemental abundances as
the structure code. We use atmospheres generated from the \texttt{MARCS} grid
of model atmospheres \citep{Plez2008}. \texttt{MARCS} provides one-dimensional,
hydrostatic, plane-parallel and spherical LTE atmospheric models
\citep{Gustafsson2008}. Model atmospheres are made to match the
spectroscopically measured elemental abundances of populations A and E.
Moreover, for each populations, atmospheres with  various helium mass fractions
are generated. These range from Y=0.24 to Y=0.36 in steps of 0.02. All
atmospehric models are computed to an optical depth of $\tau = 100$ where their
temperature and pressures serves as boundary conditions for the strudcure code.
A comparison of the pressure and temperature throughout the atmospheres of the
two populations with helium abundances representative of literature values is
shown
in Figure \ref{fig:AEAtmComp}.

\begin{figure}
	\centering
	\includegraphics[width=0.5\textwidth]{src/figures/notebookFigures/AtmosphereComparison.pdf}
	\label{fig:AEAtmComp}
	\caption{Comparison of the MARCS model atmospheres generated for the two
	extreme populations of NGC 2808. These lines shows population A and E with
	the same Helium abundance; though, we fit a grid of models over various
	helumn abundances. Dashed lines show the temperature of the boundary
	condition while sold lines show the pressure.}
\end{figure}

\subsection{Opacities}\label{sec:opac}
In addition to the atmospheric boundary conditions, both the high and low
temperature opacities used by DSEP must be made chemically consistent. Here we
use OPLIB high temperature opacity tables \citep{Colgan2016} retrieved using
the TOPS web-interface. Low temperature opacity tables are retrieved from the
Aesopus 2.0 web-interface \citep{Marigo2009, Marigo2022}. Ideally, these
opacities would be the same used in the atmospheric models. However, the
opacities used in the MARCS models are not publicly available. As such, we use
the opacities provided by the TOPS and Aesopus 2.0 web-interfaces.

>>>>

\subsection{Atmospheric Boundary Conditions}\label{sec:atm}
Certain assumptions, primarily that the radiation field is at equilibrium and
radiative transport is diffusive \citep{Salaris2005}, made in stellar structure
codes, such as DSEP, are valid when the optical depth of a star is large.
However, in the atmospheres of stars, the number density of particles drops low
enough and the optical depth consequently becomes small enough that these
assumptions break down, and separate, more physically motivated, plasma
modeling code is required. Generally structure code will use tabulated
atmospheric boundary conditions generated by these specialized codes, such as ATLAS9
\citep{Kurucz1993}, PHOENIX \citep{Husser2013}, MARCS \citep{Gustafsson2008},
and MPS-ATLAS \citep{Kostogryz2023}. Often, as the boundary conditions are
expensive to compute, they are not updated as interior abundances vary.

One key element when chemically consistently modeling NGC 2808 modeling is the
incorporation of new atmospheric models with the same elemental abundances as
the structure code. We use atmospheres generated from the \texttt{MARCS} grid
of model atmospheres \citep{Plez2008}. \texttt{MARCS} provides one-dimensional,
hydrostatic, plane-parallel and spherical LTE atmospheric models
\citep{Gustafsson2008}. Model atmospheres are made to match the
spectroscopically measured elemental abundances of populations A and E.
Moreover, for each population, atmospheres with various helium mass fractions
are generated. These range from Y=0.24 to Y=0.36 in steps of 0.03. All
atmospheric models are computed to an optical depth of $\tau = 100$ where their
temperature and pressures serves as boundary conditions for the structure code.
In general, enhancing helium in the atmosphere has only a small impact on the atmospheric
temperature profile, while leading to a drop in the pressure by $\sim 10 - 20 \%$.

\subsection{Opacities}\label{sec:opac}
In addition to the atmospheric boundary conditions, both the high and low
temperature opacities used by DSEP must be made chemically consistent. Here we
use OPLIB high temperature opacity tables \citep{Colgan2016} retrieved using
the TOPS web-interface. Retrival of High termperature opacities is done using
\texttt{pyTOPSScrape}, first introduced in \citet{Boudreaux2023}. Low
temperature opacity tables are retrieved from the Aesopus 2.0 web-interface
\citep{Marigo2009, Marigo2022}. Ideally, these opacities would be the same used
in the atmospheric models. However, the opacities used in the MARCS models are
not publicly available. As such, we use the opacities provided by the TOPS and
Aesopus 2.0 web-interfaces.

### 2024-02-03 ArXiv/intro.tex
Final copy edits of NGC 2808 paper before submission

\section{Introduction}\label{sec:Intro}
Globular clusters (GCs) are among the oldest observable objects in the
universe \citep{Pen11}. They are characterized by high densities with typical
half-light radii of $\le$10 pc \citep{Vanderburg2010}, and typical masses
ranging from $10^{4}$--$10^{5}$ M$_{\odot}$ \citep{Bro06} --- though some GCs
are significantly larger than these typical values {\color{red}EXAMPLE}. GCs
provide a unique way to probe stellar evolution \citep{Bau03}, galaxy formation
models \citep{Boy18,Kra05}, and dark matter halo structure \citep{Hud18}.
{\color{red} BRING IN SOME MORE RECENT CITATIONS.}

The traditional view of Globular Clusters was, for a long time, that they
consisted of a single stellar population (SSP, in some publications this is
referred to as a Simple Stellar Population). This view was supported by
spectroscopically uniform heavy element abundances \citep{Carretta2010, Bastian2018} accross most clusters (M54 and $\omega$Cen are notable exceptions, see \citet{Marino2015} for further details), and the lack of evidence for multiple stellar populations
(MPs) in past color-magnitude diagrams of GCs \citep[i.e.][]{Sandage1953, Alcaino1975}. However, over the last 40 years non-trivial star-to-star light-element abundance variations have been observed \citep[i.e.][]{Smith1987} and, in
the last two decades, it has been definitively shown that most if not all Milky
Way GCs have MPs \citep{Gratton2004, Gratton2012, Piotto2015}. The lack of photometric evidence for MPs
can be attributed to the short color throw available to ground based
photometric surveys \citep{Milone2017}; specifically, lacking UV filters. While MPs are chemically distinct
from one another, that distinction is most prominent when observing with $U$
and $B$ filters \citep{Sbordone2011}.

The prevalence of multiple populations in GCs is so distinct that the proposed
definitions for what constitutes a globular cluster now often center the
existence of MPs. Whereas, people have have often tried to categorized objects
as GCs through relations between half-light radius, density, and surface
brightness profile, in fact many objects which are generally thought of as GCs
don't cleanly fit into these cuts \citep{Peebles1968, Brown1991, Brown1995, Bekki2002}.
Consequently, \citet{Carretta2010} proposed a definition of GC based on
observed chemical inhomogeneities in their stellar populations. The modern
understanding of GCs then is not simply one of a dense cluster of stars which
may have chemical inhomogeneities and multiple populations; rather, it is one
where those chemical inhomogeneities and multiple populations themselves are
the defining element of a GC.

All Milky Way globular clusters older than 2 Gyr studied in detail show
populations enriched in He, N, and Na while also being deplete in O and C
\citep{Piotto2015,Bastian2018}. These light element abundance patterns also are
not strongly correlated with variations in heavy element abundance, resulting
in spectroscopically uniform Fe abundances between populations. Further,
high-resolution spectral studies reveal anti-correlations between N-C
abundances, Na-O abundances, and potentially Al-Mg \citep{Sneden1992,
Gratton2012}. Typical stellar fusion reactions can deplete core oxygen;
however, the observed abundances of Na, Al, and Mg cannot be explained by the
likes of the CNO cycle \citep{Prantzos2007}.

@@

Hot hydrogen burning (proton capture), material transport to the surface, and
material ejection into the intra-cluster media are features of each of these
models and consequently they can all be made to {\it qualitatively} agree with
the observed elemental abundances. However, none of the standard models can
currently account for all specific abundances \citep{Gratton2012}. AGB and FRMS
models are the most promising; however, both models have difficulty reproducing
severe O depletion \citep{Ventura2009,Decressin2007}. Moreover, AGB and FRMS
models require significant mass loss ($\sim 90\%$) between cluster formation
and the current epoch --- implying that a significant fraction of halo stars
formed in GCs \citep{Renzini2008,DErcole2008,Bastian2015}.

In addition to the light-element anti-correlations observed it is also known
that younger populations are significantly enhanced in Helium
\citep{Piotto2007, Piotto2015, Latour2019}. Depending on the cluster, Helium
mass fractions as high as $Y=0.4$ have been inferred \citep[e.g][]{Milone2015}.
However, due to the relatively high and tight temperature range of partial
ionization for He it cannot be observed in globular clusters; consequently, the
evidence for enhanced He in GCs originates from comparison of theoretical
stellar isochrones to the observed color-magnitude-diagrams of globular
clusters. Therefore, a careful handling of chemistry is essential when modeling
with the aim of discriminating between MPs; yet, only a very limited number of
GCs have yet been studied with chemically self-consistent (structure and
atmosphere) isochrones \citep[e.g.][NGC 6752]{Dotter2015}.

NGC 2808 is the prototype globular cluster to host Multiple Populations.
Various studies since 2007 have identified that it may host anywhere from 2-5
stellar populations. These populations have been identified both
spectroscopically \citep[i.e.][]{} and photometrically \citep[i.e.][]{}. Note
that recent work \citep{Valle2022} calls into question the statistical
significance of the detections of more than 2 populations in the spectroscopic
data. Here we present new, chemically self-consistent modeling of the
photometry of the two extreme populations of NGC 2808 identified by
\citet{Milone2015}, populations A and E. We use archival photometry from the
Hubble UV Globular Cluster Survey (HUGS) \citep{Piotto2015, Milone2017} in the
F275W and F814W passbands to charecterize multiple populations in NGC 2808
\citep{Milone2015, Milone2015b}. Additionally, we present a likelihood analysis of the
photometric data of NGC 2808 to determine the number of populations present in
the cluster.

>>>>

\section{Introduction}\label{sec:Intro}
Globular clusters (GCs) are among the oldest observable objects in the universe
\citep{Pen11}. They are characterized by high densities with typical half-light
radii of $\le$10 pc \citep{Vanderburg2010}, and typical masses ranging from
$10^{4}$--$10^{5}$ M$_{\odot}$ \citep{Bro06} --- though some GCs are
significantly larger than these typical values \citep[e.g. $\omega$ Cen,
][]{Richer1991}. GCs provide a unique way to probe stellar evolution
\citep{Bau03}, galaxy formation models \citep{Boy18,Kra05}, and dark matter
halo structure \citep{Hud18}.

The traditional view of Globular Clusters was that they consisted of a single
stellar population (SSP, in some publications this is referred to as a Simple
Stellar Population). This view was supported by spectroscopically uniform heavy
element abundances \citep{Carretta2010, Bastian2018} across most clusters (M54
and $\omega$Cen are notable exceptions, see \citet{Marino2015} for further
details), and the lack of evidence for multiple stellar populations (MPs) in
past color-magnitude diagrams of GCs \citep[i.e.][]{Sandage1953, Alcaino1975}.
However, over the last 40 years non-trivial star-to-star light-element
abundance variations have been observed \citep[i.e.][]{Smith1987} and, in the
last two decades, it has been definitively shown that most if not all Milky Way
GCs have MPs \citep{Gratton2004, Gratton2012, Piotto2015}. The lack of
photometric evidence for MPs prior to the 2000, can be attributed to the more
narrow color bands available, until very recently, to ground based photometric
surveys \citep{Milone2017}.

The prevalence of multiple populations in GCs is so distinct that the proposed
definitions for what constitutes a globular cluster now often center the
existence of MPs \citep[e.g.][]{Carretta2010}. Whereas, people have have often tried to categorized objects
as GCs through relations between half-light radius, density, and surface
brightness profile, in fact many objects which are generally thought of as GCs
don't cleanly fit into these cuts \citep{Peebles1968, Brown1991, Brown1995, Bekki2002}.
Consequently, \citet{Carretta2010} proposed a definition of GC based on
observed chemical inhomogeneities in their stellar populations. The modern
understanding of GCs then is not simply one of a dense cluster of stars that
may have chemical inhomogeneities and multiple populations; rather, it is one
where those chemical inhomogeneities and multiple populations themselves are
the defining element of a GC.

All Milky Way globular clusters older than 2 Gyr studied in detail show
populations enriched in He, N, and Na while also being deplete in O and C
\citep{Piotto2015,Bastian2018}. These light element abundance patterns also are
not strongly correlated with variations in heavy element abundance, resulting
in spectroscopically uniform Fe abundances between populations. Further,
high-resolution spectral studies reveal anti-correlations between N-C
abundances, Na-O abundances, and potentially Al-Mg \citep{Sneden1992,
Gratton2012}. Typical stellar fusion reactions can deplete core oxygen;
however, the observed abundances of Na, Al, and Mg cannot be explained by the
CNO cycle \citep{Prantzos2007}. Consequently, globular cluster populations must
be formed by some novel means.

@@

Hot hydrogen burning (i.e. proton capture), material transport to the surface, and
material ejection into the intra-cluster media are features of each of these
models and consequently they can all be made to {\it qualitatively} agree with
the observed elemental abundances. However, none of the standard models can
currently account for all specific abundances \citep{Gratton2012}. AGB and FRMS
models are the most promising; however, both models have difficulty reproducing
severe O depletion \citep{Ventura2009,Decressin2007}. Moreover, AGB and FRMS
models require significant mass loss ($\sim 90\%$) between cluster formation
and the current epoch --- implying that a significant fraction of halo stars
formed in GCs \citep{Renzini2008,DErcole2008,Bastian2015}.

In addition to the light-element anti-correlations observed, it is also known
that younger populations are significantly enhanced in Helium
\citep{Piotto2007, Piotto2015, Latour2019}. Depending on the cluster, helium
mass fractions as high as $Y=0.4$ have been inferred \citep[e.g][]{Milone2015}.
However, due to both the relatively high and tight temperature range of partial
ionization for He and the efficiency of gravitational settling in core helium
burning stars, the initial He abundance of globular cluster stars cannot be
observed; consequently, the evidence for enhanced He in GCs originates from
comparison of theoretical stellar isochrones to the observed
color-magnitude-diagrams of globular clusters. Therefore, a careful handling of
chemistry is essential when modeling with the aim of discriminating between
MPs; yet, only a very limited number of GCs have been studied with
chemically self-consistent (structure and atmosphere) isochrones
\citep[e.g.][NGC 6752]{Dotter2015}.

NGC 2808 is the prototype globular cluster to host Multiple Populations.
Various studies since 2007 have identified that it may host anywhere from 2-5
stellar populations. These populations have been identified both
spectroscopically \citep[i.e.][]{Carretta2004, Carretta2006, Carretta2010, Gratton2011, Carretta2015, Hong2021} and photometrically \citep[i.e.][]{Piotto2007, Piotto2015, Milone2015, Milone2017, Pasquato2019}. Note
that recent work \citep{Valle2022} calls into question the statistical
significance of the detections of more than 2 populations in the spectroscopic
data. Here we present new, chemically self-consistent modeling of the
photometry of the two extreme populations of NGC 2808 identified by
\citet{Milone2015}, populations A and E. We use archival photometry from the
Hubble UV Globular Cluster Survey (HUGS) \citep{Piotto2015, Milone2017} in the
F275W and F814W passbands to characterize multiple populations in NGC 2808
\citep{Milone2015, Milone2015b}. Additionally, we present a likelihood analysis of the
photometric data of NGC 2808 to determine the number of populations present in
the cluster.
